Towards a Planckian standard kilogram: a scenario for measuring $G$ using an artificial two-body orbit

### 2018-04-03 msrsos.tex
RSOS format

%\documentclass[referee]{aa} % for a referee version
\documentclass[onecolumn]{aa} % for a paper on 1 column  
%\documentclass[longauth]{aa} % for the long lists of affiliations 
%\documentclass[letter]{aa} % for the letters 
%\documentclass[bibyear]{aa} % if the references are not structured 
%                              according to the author-year natbib style
%\documentclass{aa}

@@

\title{Towards a Planckian standard kilogram}
\subtitle{}

\author{Michael Ebersold\thanks{michael.ebersold@uzh.ch}%\inst{1}
        \and
        Prasenjit Saha%\inst{2}\fnmsep
       }

\institute{Physik-Institut, University of Zurich, Winterthurerstrasse
  190, 8057 Zurich, Switzerland}

\date{}

\abstract
% context heading (optional)
% {} leave it empty if necessary  
{As the kilogram assumes its new definition in terms of $h,c,$ and the
  standard second, it is interesting to think about a possible future
  definition entirely in terms of fundamental constants.  A kilogram
  defined as an integer multiple of the Planck mass (or
  4594xxxx$\times\sqrt{\hbar c/G}$) would cause no significant change
  from its current value.}
% aims heading (mandatory)
{The practical hurdle to this Planckian kilogram is measuring $G$
  three or four orders of magnitude better than currently known, so as
  to find the unknown digits xxxx.  We study a possible scenario for
  doing so with an artificial two-body orbit.}
% methods heading (mandatory)
{The cleanest (admittedly, not the cheapest) option is to place the
  system on a Trojan orbit to minimize external gravitational
  perturbations, and enclose it in a cavity chilled to liquid-helium
  temperatures, to suppress radiation pressure.}
% results heading (mandatory)
{Data analysis would involve marginalizing over at least 15~nuisance
  parameters (6~for orbital parameters and 9~for fictitious forces)
  but that, we show, is feasible.}
% conclusions heading (optional), leave it empty if necessary 
{}

\keywords{}

@@

\bibliographystyle{aa}
\bibliography{ms.bib}

@@

>>>>

\documentclass[]{rsos}

@@

%%%% Article title to be placed here
\title{Towards a Planckian standard kilogram:
a scenario for measuring $G$ using an artificial two-body orbit}

\author{Michael Ebersold and Prasenjit Saha}

\address{Physik-Institut, University of Zurich, Winterthurerstrasse
  190, 8057 Zurich, Switzerland}

\subject{xxxxx, xxxxx, xxxx}

\keywords{xxxx, xxxx, xxxx}

\corres{Michael Ebersold\\
\email{michael.ebersold@uzh.ch}}

\begin{abstract}
{As the kilogram assumes its new definition in terms of $h,c,$ and the
  standard second, it is interesting to think about a possible future
  definition entirely in terms of fundamental constants.
  A kilogram could, in principle, be defined as an integer multiple of
  the Planck mass (or 4594????$\times\sqrt{\hbar c/G}$) without
  significantly altering its current value.  The practical hurdle is
  measuring $G$ four orders of magnitude better than currently known,
  in order to fix the four unknown digits.}
{We assess the prospects for measuring $G$ to the desired accuracy
  using an artificial two-body orbit.}
{The cleanest (admittedly, not the cheapest) option is to place the
  system on a Trojan orbit to minimize external gravitational
  perturbations, and enclose it in a cavity chilled to liquid-helium
  temperatures, to suppress radiation pressure.}
{Data analysis would involve marginalizing over at least 15~nuisance
  parameters (6~for orbital parameters and 9~for fictitious forces)
  but that, we show, is feasible.}
{A more complicated system in Earth orbit should be taken seriously.}
\end{abstract}

@@

\def\nat{Nature}
\def\prd{PRD}

\bibliographystyle{RS}
\bibliography{ms.bib}

@@

%%%%%%%%%% Insert the texts which can accomdate on firstpage in the tag "fmtext" %%%%%

\begin{fmtext}

\section{Insert A head here}
%%%% Insert A head here

This demo file is intended to serve as a ``starter file''
for rsproca journal papers produced under \LaTeX\ using
rsproca.cls v1.5e.

\subsection{Insert B head here}
%%%% Insert B head here
Subsection text here.

\subsubsection{Insert C head here}
%%%% Insert C head here
Subsubsection text here.

\section{Equations}

Sample equations. \cite{1}\cite{1,2} \cite{1,2,3}

%%% Numbered equation
\begin{align}\label{1.1}
\begin{split}
\frac{\partial u(t,x)}{\partial t} &= Au(t,x) \left(1-\frac{u(t,x)}{K}\right)-B\frac{u(t-\tau,x) w(t,x)}{1+Eu(t-\tau,x)},\\
\frac{\partial w(t,x)}{\partial t} &=\delta \frac{\partial^2w(t,x)}{\partial x^2}-Cw(t,x)+D\frac{u(t-\tau,x)w(t,x)}{1+Eu(t-\tau,x)},
\end{split}
\end{align}

\begin{align}\label{1.2}
\begin{split}
\frac{dU}{dt} &=\alpha U(t)(\gamma -U(t))-\frac{U(t-\tau)W(t)}{1+U(t-\tau)},\\
\frac{dW}{dt} &=-W(t)+\beta\frac{U(t-\tau)W(t)}{1+U(t-\tau)}.
\end{split}
\end{align}

%%%% Unnumbered equation
\begin{eqnarray}
\frac{\partial(F_1,F_2)}{\partial(c,\omega)}_{(c_0,\omega_0)} = \left|
\begin{array}{ll}
\frac{\partial F_1}{\partial c} &\frac{\partial F_1}{\partial \omega} \\\noalign{\vskip3pt}
\frac{\partial F_2}{\partial c}&\frac{\partial F_2}{\partial \omega}
\end{array}\right|_{(c_0,\omega_0)}\notag\\
=-4c_0q\omega_0 -4c_0\omega_0p^2 =-4c_0\omega_0(q+p^2)>0.
\end{eqnarray}
\end{fmtext}

%%%%%%%%%%%%%%% End of first page %%%%%%%%%%%%%%%%%%%%%

\section{Enunciations}

\begin{theorem}\label{T0.1}
Assume that $\alpha>0, \gamma>1, \beta>\frac{\gamma+1}{\gamma-1}$.
Then there exists a small $\tau_1>0$, such that for $\tau\in
[0,\tau_1)$, if $c$ crosses $c(\tau)$ from the direction of
to  a small amplitude periodic traveling wave solution of
(2.1), and the period of $(\check{u}^p(s),\check{w}^p(s))$ is
\[
\check{T}(c)=c\cdot \left[\frac{2\pi}{\omega(\tau)}+O(c-c(\tau))\right].
\]
\end{theorem}

\begin{condition}\label{C2.2}
From (0.8) and (2.10), it holds
$\frac{d\omega}{d\tau}<0,\frac{dc}{d\tau}<0$ for $\tau\in
[0,\tau_1)$. This fact yields that the system (2.1) with delay
$\tau>0$ has the periodic traveling waves for smaller wave speed $c$
than that the system (2.1) with $\tau=0$ does. That is, the
delay perturbation stimulates an early occurrence of the traveling waves.
\end{condition}

\section{Figures \& Tables}

The output for figure is:

\begin{figure}[!h]
%\centering\includegraphics[width=2.5in]{xxxxxx.eps}
%%% where xxxxxx name represents "figurename.eps"
\caption{Insert figure caption here}
\label{fig_sim}
\end{figure}

\vspace*{-10pt}

\noindent The output for table is:

\begin{table}[!h]
\caption{An Example of a Table}%%%Table caption goes here
\label{table_example}
\begin{tabular}{llll}%%%The number of columns has to be defined here
\hline
date &Dutch policy &date &European policy \\
\hline
1988 &Memorandum Prevention &1985 &European Directive (85/339) \\
1991--1997 &{\bf Packaging Covenant I} & & \\
1994 &Law Environmental Management &1994 &European Directive (94/62) \\
1997 &Agreement Packaging and Packaging Waste & & \\
1998--2002 &{\bf Packaging Covenant II} & & \\
2003--2005 &{\bf Packaging Covenant III} & & \\
2006--2007 &{\bf Decree on Packaging and paper} & & \\\hline
\end{tabular}
\end{table}%%%End of the table

\section{Conclusion}
The conclusion text goes here.

\vskip1pc

\ethics{Insert ethics text here.}

\dataccess{Insert data accessibility text here. '(If no information, then please include the text ``This article has no additional data'').}

\aucontribute{Insert author contributions text here (to be included if more than one author).}

\competing{Insert competing interests text here.}

\funding{Insert funding text here.}

\ack{Insert acknowledgment text here.}

\disclaimer{Insert disclaimer text here.}

\pagebreak

%%%%%%%%%% Insert bibliography here %%%%%%%%%%%%%%

\noindent {\bf Please follow the coding for references as shown below.}

\begin{thebibliography}{9}

\bibitem{1} Allwood JM, Cullen JM. 2011 \textit{Sustainable materials:  with both eyes open}.
Cambridge, UK: UIT Cambridge. See \href{http://www.withbotheyesopen.com}{http://www.withbotheyesopen.com}.

\bibitem{2}  MacKay DJC. 2008  \textit{Sustainable energy:  without the hot air}.
 Cambridge, UK: UIT Cambridge. See \href{http://www.withouthotair.com}{http://www.withouthotair.com}.

\bibitem{3} Gallman PG. 2011  \textit{Green alternatives and national energy strategy: the facts
 behind the headlines}.  Baltimore,\ MD: Johns Hopkins University Press.

\bibitem{4} MacKay DJC. 2013.  Solar energy in the context of energy use, energy transportation, and
 energy storage. \textit{Proc. R. Soc. A} \textbf{371}.

\end{thebibliography}

\vskip2pc

\noindent If maintaining .bib file for references, then please use "RS.bst" to generate the references.

\noindent Example:

\verb+\bibliographystyle{RS}+ %%%% .BST file

\verb+\bibliography{sample}+ %%%%% .Bib file
